---
title: "Network Comparison"
author: "Benjamin A Logsdon"
date: "3/20/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(cache = TRUE)
```

## Grab Networks from Synapse
First we query the private collaboration space (syn2370594) for networks where the method is defined as bic - the sparse metanetworks, and reduce down to columns of interest with dplyr select.
```{r query, message=FALSE, warning=FALSE}
synapseClient::synapseLogin()
foo <- synapseClient::synQuery('select * from file where method==\'bic\' and projectId==\'syn2370594\'')
bar <- dplyr::select(foo,file.name,file.id,file.versionComment)
bar
```

Next, we load the networks into R and name them appropriately, and grab the number of edges each network has to append to the network manifest.

```{r load, message=FALSE, warning=FALSE}
loadBic <- function(synId){
  synapseClient::synapseLogin()
  foo<-synapseClient::synGet(synId)
  load(foo@filePath)
  return(bicNetworks$network)
}
library(Matrix)
ampNetworks <- lapply(bar$file.id,loadBic)
names(ampNetworks) <- c('mayoCer',
                        'mssmFp',
                        'mssmStg',
                        'mssmPhg',
                        'mssmIfg',
                        'mayoTcx',
                        'mcadgsTCX',
                        'mcadgsCER',
                        'rosmap')
rownames(bar) <- names(ampNetworks)
nedges <- sapply(ampNetworks,function(x) sum(x))
bar$nedges <- nedges
bar

```

We'll want to convert the networks to full sparse adjacency matrices (not just upper diagonal sparse matrices).

```{r modifyNet}
makeFull <- function(x){
  gc()
  x <- as.matrix(x)
  x <- x+t(x)
  x <- Matrix::Matrix(x,sparse = TRUE)
  return(x)
}
ampNetworks <- lapply(ampNetworks,makeFull)
ampNetworks$rosmap[1:5,1:5]
```

## Network comparison
Next, we create a manifest of all pairwise comparisons between each type of network.


```{r manifest, message=FALSE, warning=FALSE}
library(dplyr)
methodManifest <- combn(names(ampNetworks),2) %>% t
colnames(methodManifest) <- c('network1','network2')
methodManifest <- data.frame(methodManifest,
                             stringsAsFactors=F)
head(methodManifest)
```

We're going to use this manifest to iterate over all pairwise comparisons between networks.  We'll do so using a function in the metanetwork package that computes a Fisher's exact test for overlap of edge sets between networks, along with some other summary statistics.  We'll use a wrapper function to do the parameter handling.

```{r comparison}

wrapperFxn <- function(method1,method2,allnets){
  cat('method1:',method1,'method2:',method2,'\n')
  return(metanetwork::compareTwoNetworks(allnets[[method1]],allnets[[method2]]))
}

networkCompare <- mapply(wrapperFxn,
                         methodManifest[,1],
                         methodManifest[,2],
                         MoreArgs = list(allnets=ampNetworks),
                         SIMPLIFY = FALSE)
```


Next, we fill out the pairwise comparison manifest with relevant statistics from the pairwise comparison, and properties of the networks.

```{r manifest2}
grabOddsRatios <- function(x){
  return(x[[1]]$estimate)
}
grabPvalue <- function(x){
  return(x[[1]]$p.value)
}
getSynIds <- function(x,networkManifest){
  return(networkManifest[x,'file.id'])
}
getNetwork1Overlap <- function(x){
  return(x[[2]])
}
getNetwork2Overlap <- function(x){
  return(x[[3]])
}
getNedges <- function(x,networkManifest){
  return(networkManifest[x,'nedges'])
}

ors <- sapply(networkCompare,grabOddsRatios)
pvals <- sapply(networkCompare,grabPvalue)
network1synId <- sapply(methodManifest$network1,getSynIds,bar)
network2synId <- sapply(methodManifest$network2,getSynIds,bar)
network1Overlap <- sapply(networkCompare,getNetwork1Overlap)
network2Overlap <- sapply(networkCompare,getNetwork2Overlap)
#colnames(methodManifest) <- c('network1','network2')
#methodManifest <- data.frame(methodManifest,
#                             stringsAsFactors = F)
methodManifest$ors <- ors
methodManifest$network1synId <- network1synId
methodManifest$network2synId <- network2synId
methodManifest$network1Overlap <- network1Overlap
methodManifest$network2Overlap <- network2Overlap
methodManifest$network1Nedges <- sapply(methodManifest$network1,getNedges,bar)
methodManifest$network2Nedges <- sapply(methodManifest$network2,getNedges,bar)

head(methodManifest)
```

## Push manifest to Synapse
Next, let's push the manifest of pariwise comparisons to Synapse as a csv file and as a table.

```{r synapse, message=FALSE, warning=FALSE}
storageFolderId <- 'syn8449629'
permLink1 <- githubr::getPermlink(repository = 'Sage-Bionetworks/AMP-AD_Network_Analysis',
                               ref = 'branch',
                               refName = 'comparisons',
                               repositoryPath = 'networkComparison.Rmd')

permLink2 <- githubr::getPermlink(repository = 'Sage-Bionetworks/metanetwork',
                               ref = 'branch',
                               refName = 'dev',
                               repositoryPath = 'R/compareTwoNetworks.R')

permLink3 <- githubr::getPermlink(repository = 'Sage-Bionetworks/rSynapseUtilities',
                               ref = 'branch',
                               refName = 'dev',
                               repositoryPath = 'R/pushToSynapseWrapper.R')

manifestFileName <- 'metanetworkTopologyPairwiseComparison.csv'

annots <- list(fileType='csv',
  summaryLevel='gene',
  organism='HomoSapiens',
  dataType='analysis',
  analysisType='networkTopologyComparison')

comments <- "Pairwise comparison between each pairs of rank consensus sparse networks from AMP-AD expression data"

usedids <- as.list(bar$file.id)

executedurls <- as.list(c(permLink1,permLink2,permLink3))

activitys <- "Pairwise Coexpression Topology Comparison"

activityDescription <- "Compare all pairs of coexpression network topologies."

comparisonObj = rSynapseUtilities::pushToSynapseWrapper(df=methodManifest,
                                     fileName=manifestFileName,
                                     synapseFolderId=storageFolderId,
                                     annos=annots,
                                     comment=comments,
                                     usedVector=usedids,
                                     executedVector=executedurls,
                                     activityName1=activitys,
                                     activityDescription1=activityDescription)

rSynapseUtilities::makeTable(df=methodManifest,
                             tableName='Pairwise Sparse Metanetwork Topology Comparison',
                             projectId='syn2370594')

```


## Visualizations
Next, let's make some plots that will help us understand the relationships between the network topologies, first a pca plot

```{r plots, echo=FALSE}
methodManifest2 <- dplyr::select(methodManifest,network1,network2,ors)
distMat <- tidyr::spread(methodManifest2,
                         network1,
                         ors)
rownames(distMat) <- distMat$network2
distMat <- dplyr::select(distMat,-network2)
missingRow <- setdiff(colnames(distMat),rownames(distMat))
missingCol <- setdiff(rownames(distMat),colnames(distMat))
distMat[,missingCol] <- NA
distMat[missingRow,] <- NA
distMat <- distMat[,rownames(distMat)]
distMat[(is.na(distMat))] <- 0
distMat2 <- distMat + t(distMat)
View(distMat2)
svd2 <- svd(distMat2)
library(wesanderson)

makePcPlot <- function(svdecomp,i,j,nameVec){
  rangex <- max(svd2$u[,i])-min(svd2$u[,i])
  rangey <- max(svd2$u[,j])-min(svd2$u[,j])
  xmin <- min(svd2$u[,i])-0.10*rangex
  xmax <- max(svd2$u[,i])+0.10*rangex
  ymin <- min(svd2$u[,j])-0.10*rangey
  ymax <- max(svd2$u[,j])+0.10*rangey
  plot(svd2$u[,i],
       svd2$u[,j],
       col='white',
       xlim=c(xmin,xmax),
       ylim=c(ymin,ymax),
       xlab = paste0('PCA',i),
       ylab = paste0('PCA',j))
  text(svd2$u[,i],
       svd2$u[,j],
       nameVec,
       col=wes_palette("Rushmore",7,type='continuous'))
}
makePcPlot(svd2,1,2,rownames(distMat))
#par(mar=c(12,4,6,6))

```

next a heatmap of odds ratios of pairwise comparisons

```{r heatmap,echo=FALSE}
pheatmap::pheatmap(distMat2)
```